\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-09-16 NAR_DRAFT.tex
more typos and things that don't work corrected

\begin{figure}
  \begin{center}
  \includegraphics{figures/signatures_only.pdf}
  \end{center}
  \caption{Tumor mutation profiles.
  In each panel, the y-axis is the proportion of total mutations in the tumor with each of the 96 substitution types shown on the x-axis.
  \textbf{(A)} The observed mutation profile of an acute myeloid leukemia used in our real data analysis \cite{Griffith2015}.
  \textbf{(B)} The observed mutation profile of a breast tumor we used in our real data analysis \cite{Shi2018}.
  \textbf{(C)} A mutation profile used for simulating tumors, made up of equal proportions of COSMIC mutation signatures 1, 7, \& 11.
  \textbf{(D)} Equal proportions of signatures 1, 4, \& 5.
  \textbf{(E)} Equal proportions of signatures 1, 3, \& 5.
  \textbf{(F)} The observed mutaiton profile of a real breast tumor obtained from supplementary materials in Alexandrov et al., 2019 \citep{Alexandrov2019}.
  \textbf{(G)} The observed mutaiton profile of a real breast tumor obtained from supplementary materials in Alexandrov et al., 2019 \citep{Alexandrov2019}.
  }
  \label{NAR-sigfig}
 \end{figure}

@@

\subsection{Estimation of the mutation rate.}
The final piece of equation \ref{eqn:detailed_prior} to specify is $p(M)$, the prior probability that a mutation will occur at a given site, which we specify as the per-base mutation rate $\mu$.
In an exponentially growing and neutrally or nearly neutrally evolving tumor, \citet{Williams2018} show that the total number of mutations $\mathrm{M}$ between two allele frequencies ($f_{min}$,$f_{max}$) is
\begin{equation}
  \label{eqn:mut_rate}
$$
  \mathrm{M}(f_{min},f_{max}) = N\frac{\mu}{\beta}\left(\frac{1}{f_{min}} - \frac{1}{f_{max}}\right).
$$
\end{equation}

>>>>

\begin{figure}
  \begin{center}
  \includegraphics{figures/signatures_only.pdf}
  \end{center}
  \caption{Tumor mutation profiles.
  In each panel, the y-axis is the proportion of total mutations in the tumor with each of the 96 substitution types shown on the x-axis.
  \textbf{(A)} The observed mutation profile of an acute myeloid leukemia used in our real data analysis \cite{Griffith2015}.
  \textbf{(B)} The observed mutation profile of a breast tumor we used in our real data analysis \cite{Shi2018}.
  \textbf{(C)} A mutation profile used for simulating tumors, made up of equal proportions of COSMIC mutation signatures 1, 7, \& 11.
  \textbf{(D)} Equal proportions of signatures 1, 4, \& 5.
  \textbf{(E)} Equal proportions of signatures 1, 3, \& 5.
  \textbf{(F)}--\textbf{(G)} The observed mutation profile of two real breast tumors obtained from supplementary materials in Alexandrov et al., 2019 \citep{Alexandrov2019}.
  }
  \label{NAR-sigfig}
 \end{figure}

@@

\subsection{Estimation of the mutation rate.}
The final piece of equation \ref{eqn:detailed_prior} to specify is $p(M)$, the prior probability that a mutation will occur at a given site, which we specify as the per-base mutation rate $\mu$.
In an exponentially growing and neutrally or nearly neutrally evolving tumor, Williams et al. 2018~\citep{Williams2018} show that the total number of mutations $\mathrm{M}$ between two allele frequencies ($f_{min}$,$f_{max}$) is
\begin{equation}
  \label{eqn:mut_rate}
$$
  \mathrm{M}(f_{min},f_{max}) = N\frac{\mu}{\beta}\left(\frac{1}{f_{min}} - \frac{1}{f_{max}}\right).
$$
\end{equation}
